Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-12 latex/comp_or.tex
Performance plots added

\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage{algorithm} % sudo apt-get install -y texlive-science

@@

\begin{table}[H]
	\centering
	\caption{Performance for different number of concurrent processes with $1.2 \times volume$}  \label{tab:procs}
%	\footnotesize
	\scriptsize
	\begin{tabular}{c| c | c | c c c c c c }
	\toprule
	\textbf{Scenario} & $method$ &{\bf Results}     & \textbf{1} & \textbf{4} & \textbf{8} & \textbf{16} & \textbf{24} & \textbf{32}  \\
	\toprule
	\multirow{4}{*}{\bf {1}}  &\multirow{2}{*}{\it {mpShims}}  &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &                                &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
                              \cmidrule{2-9}
	                          &\multirow{2}{*}{\it {mpACO}}    &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &                                &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
	\cmidrule{1-9}
	\multirow{4}{*}{\bf {2}}  &\multirow{2}{*}{\it {mpShims}} &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &   &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
                              \cmidrule{2-9}
	                          &\multirow{2}{*}{\it {mpACO}}   &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &   &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\				
	\bottomrule		
\end{tabular}

@@

@@

		\multirow{2}{*}{\it {ACO}}     &\multirow{2}{*}{\bf {1}} & $f$              & 5.77        & 3.49    &          &        &       &      &   \\ 
                                       &                         &{\bf run-time (s)}& 14          & 808     &           &        &       &      &   \\ 
        \midrule[.1pt]

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{Images/multithreads.png}
	\caption{sdf sdf sdf sdf}
	\small\textsuperscript{Source: sdfsdf}
	\label{fig:multithreads}
\end{figure}

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{units}
\usepackage{tikz}

\usepackage{algorithm} % sudo apt-get install -y texlive-science

@@

\begin{table}[H]
	\centering
	\caption{Performance for different number of concurrent processes with $1.2 \times volume$}  \label{tab:procs}
%	\footnotesize
	\scriptsize
	\begin{tabular}{c| c | c | c c c c c c c c }
	\toprule
	{\it Scenario} & $method$ &{\bf numProcs}    & \textbf{1} & \textbf{4} & \textbf{8} & \textbf{16} & \textbf{24} & \textbf{32} & \textbf{40} & \textbf{48}  \\
	\toprule
	\multirow{4}{*}{\it {1}}  &\multirow{2}{*}{\it {mpShims}}  &{\bf scores}      & 10909 & 10936 & 11022 & 11003 & 11033 & 11021 & 11013 & 11033 \\
	                          &                                &{\bf run-time (s)}& 0.12 & 0.23 & 0.44 & 0.65 & 1.13 & 1.74 & 2.32 & 3.68  \\
                              \cmidrule{2-11}
	                          &\multirow{2}{*}{\it {mpACO}}    &{\bf scores}               & 4 & 4 & 8 & 16 & 24 & 32&& \\
	                          &                                &{\bf run-time (s)}& 4 & 4 & 8 & 16 & 24 & 32&& \\
	\cmidrule{1-11}
	\multirow{4}{*}{\it {2}}  &\multirow{2}{*}{\it {mpShims}} &{\bf scores}       & 40016 & 40071 & 40071 & 40078 & 40078 & 40073 & 40083 & 40083 \\
	                          &                               &{\bf run-time (s)} & 2.72 & 2.85 & 2.15 & 1.95 & 3.10 & 20.32 & 13.95 & 17.24  \\
                              \cmidrule{2-11}
	                          &\multirow{2}{*}{\it {mpACO}}   &{\bf scores}       & 4 & 4 & 8 & 16 & 24 & 32&& \\
	                          &   &{\bf run-time (s)}         & 4 & 4 & 8 & 16 & 24 & 32&& \\				
	\bottomrule		
\end{tabular}

@@

%np  time    score

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				%width=\linewidth, % Scale the plot to \linewidth
				grid=major, 
				grid style={dashed,gray!30},
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				nodes near coords,
				enlargelimits=0.2,
				legend pos=south east,
				y tick label style={
						/pgf/number format/.cd,
						fixed,
						fixed zerofill,
						precision=3,
						/tikz/.cd,
					},				
				]

				\addplot +[
					only marks,
					point meta=explicit symbolic,
					nodes near coords = {$\pgfmathprintnumber[frac]\np$},
					visualization depends on={\thisrow{np} \as \np},
					font=\small,
				]
				table[x=time, y=score, col sep=comma] {mpShims1.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
~%
%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				%width=\linewidth, % Scale the plot to \linewidth
				grid=major, 
				grid style={dashed,gray!30},
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				nodes near coords,
				enlargelimits=0.2,
				legend pos=south east,
				y tick label style={
						/pgf/number format/.cd,
						fixed,
						fixed zerofill,
						precision=3,
						/tikz/.cd,
					}
				]

				\addplot +[
					only marks,
					point meta=explicit symbolic,
					nodes near coords = {$\pgfmathprintnumber[frac]\np$},
					visualization depends on={\thisrow{np} \as \np},
					font=\small,
				]
				table[x=time, y=score, col sep=comma] {mpShims2.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}

		\caption{{\it mpShims} performance on {\it Scenarios 1 and 2}.}
	\end{center}

\end{figure}\label{fig:mpShims}

Observing Figure \ref{fig:mpShims}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

@@

		\multirow{2}{*}{\it {ACO}}     &\multirow{2}{*}{\bf {1}} & $f$              & 5.77        & 3.49    & 3.02         &        &       &      &   \\ 
                                       &                         &{\bf run-time (s)}& 14          & 808     & 2398          &        &       &      &   \\ 
        \midrule[.1pt]

@@
